---
title: "Differential gene expression analysis"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
  highlight: kate
---
  
```{r setup, include=FALSE}
library(knitr)
library(rmdformats)
library(DT)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
               cache=FALSE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

## NOTE

Due to the large size of table with ~18000 rows, the initial loading of this interactive `HTML` document can take up to **2-3 minutes** or even longer. Please be patient. In case you get a **page unresponsive** message in your browser, choose to **wait** and don’t refresh the page. Refreshing the page will unnecessarily start the page reload from scratch and cause additional delays.


```{r}

#-------------------------------------------------------------------------------
# Interactive DGE tables
#-------------------------------------------------------------------------------

path = "/icgc/dkfzlsdf/analysis/B080/sharma/boulantLab/bulk_hypoxia/"
dge  = readRDS(paste0(path, "analysis/DiffExp/diffExpGenes.RDS"))

dge = lapply(dge, function(x){
  x = data.frame(x)[,c(6,1:5)]
  x[,c(2:4)] = round(x[,c(2:4)], 2)
  x$pvalue = signif(x$pvalue, 2)
  x$padj = signif(x$padj, 2)
  return (x)
})

```

## Hypoxia vs Normoxia (12hr)

```{r}

datatable(dge$T_12hr, rownames = FALSE, filter="top", class="compact",
          caption = "Differential gene expression analysis - Hypoxia vs Normoxia (12hr)",
          extensions = c('Buttons') ,
          options = list(autoWidth = TRUE,
                         dom = 'Blfrtip',
                         buttons = c('csv', 'excel')))

```
